### 2021-04-04 Chapter-3/Chapter-3.tex
update

      DES &         & 15                     & 0                   & 15                   & 4,596        & 58     \\
      DES &             & 15                     & 0                   & 15                   & 4,596        & 57      \\
      DES &         & 6                      & 0                   & 6                    & 2,976         & 163    \\
      DES &         & 8                      & 0                   & 8                    & 2,593         & 166     \\
      DES &           & 8                      & 0                   & 8                    & 2,593        & 165     \\
      DES &            & 8                      & 0                   & 8                    & 4,260         & 182     \\
      DES &       & 6                      & 0                   & 6                    & 8,272         & 229     \\

@@

      Chacha20 &           & 0                      & 0                   & 0                    & 149,353        & 2         \\  
      Poly1305 &          & 0                      & 0                   & 0                    & 1,213,937      & 15     \\
      Argon2i &          & 0                      & 0                   & 0                    & 4,595,142       & 37    \\
      Ed25519 &           & 0                      & 0                   & 0                    & 5,713,619       & 271     \\
      ECDSA &             & 6                      &    6                & 0                    &  4,214,946     &  48    \\ 
      ECDSA &            &   4                   &   4                 & 0                    &  4,192,558    & 102        \\   
      ECDSA &          &  5                    & 4                   & 1                    &  8,248,322       & 101     \\   
      ECDSA &           &  5                    & 4                   & 1                    &  8,263,599      & 100      \\   
      ECDSA &        &  5                    & 4                   & 1                    &  6,100,465       & 76     \\  
      ECDSA &           & 0                      &  0                   &    0               &  10,244,076       &  121      \\  
      ECDSA &          & 0           &  0                   &  0                 &  9,266,191          & 102    \\

                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
      RSA &           & 6                       & 6                   & 0                    & 22,109,246    & 39      \\
      RSA &            & 12                      & 12                  & 0                    & 24,484,441    & 44        \\
      RSA &           & 107                    & 105                 & 2                    & 17,002,523   & 23  \\
      RSA &           & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &           & 36                     & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & & 11& 9& 2& 9,527,231& 2 \\
      RSA & & 14& 14& 0& 10,513,606& 14  \\
      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\

>>>>

      DES &  mbedTLS 2.5     & 15                     & 0                   & 15                   & 4,596        & 58     \\
      DES &  mbedTLS 2.15           & 15                     & 0                   & 15                   & 4,596        & 57      \\
      DES &  OpenSSL 0.9.7       & 6                      & 0                   & 6                    & 2,976         & 163    \\
      DES &  OpenSSL 1.0.2f     & 8                      & 0                   & 8                    & 2,593         & 166     \\
      DES &  OpenSSL 1.0.2k     & 8                      & 0                   & 8                    & 2,593        & 165     \\
      DES &  OpenSSL 1.1.0f      & 8                      & 0                   & 8                    & 4,260         & 182     \\
      DES &   OpenSSL 1.1.1    & 6                      & 0                   & 6                    & 8,272         & 229     \\

@@

      Chacha20 &  Monocypher 3.0    & 0          & 0                   & 0                    & 149,353        & 2         \\  
      Poly1305 &  Monocypher 3.0    & 0          & 0                   & 0                    & 1,213,937      & 15     \\
      Argon2i &   Monocypher 3.0    & 0         & 0                   & 0                    & 4,595,142       & 37    \\
      Ed25519 &   Monocypher 3.0    & 0       & 0                   & 0                    & 5,713,619       & 271     \\
      ECDSA &   mbedTLS 2.5   & 6       &    6                & 0                    &  4,214,946     &  48    \\ 
      ECDSA &   mbedTLS 2.15   &   4                   &   4                 & 0                    &  4,192,558    & 102        \\   
      ECDSA &    OpenSSL 1.0.2f   &  5                    & 4                   & 1                    &  8,248,322       & 101     \\   
      ECDSA &   OpenSSL 1.0.2k     &  5                    & 4                   & 1                    &  8,263,599      & 100      \\   
      ECDSA &   OpenSSL 1.1.0f  &  5                    & 4                   & 1                    &  6,100,465       & 76     \\  
      ECDSA &   OpenSSL 1.1.1       & 0                      &  0                   &    0               &  10,244,076       &  121      \\  
      ECDSA &   OpenSSL 1.1.1g    & 0         &  0       &  0           &  9,266,191          & 102    \\

                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
      RSA &    mbedTLS 2.5   & 6            & 6          & 0                    & 22,109,246    & 39      \\
      RSA &    mbedTLS 2.15    & 12          & 12     & 0                    & 24,484,441    & 44        \\
      RSA &     OpenSSL 0.9.7      & 107     & 105           & 2                    & 17,002,523   & 23  \\
      RSA &    OpenSSL 1.0.2f      & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &   OpenSSL 1.0.2k      & 36              & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & & 11& 9& 2& 9,527,231& 2 \\
      RSA & & 14& 14& 0& 10,513,606& 14  \\
      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
